Experiment 1 Analysis

### 2023-07-25 Analysis/e1_Analysis.qmd

---
title: Experiment 1 Analysis
date: last-modified
categories: [Analysis, R]
page-layout: article
fig-width: 15
fig-height: 8
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

### Dictionary

@@

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,ggpattern)
e1 <- readRDS(here("data/e1_07_04_23.rds"))
source(here("Functions/Display_Functions.R"))

### Methods

@@

```{r design, echo=FALSE, fig.cap="Experiment Procedure"}
DiagrammeR::grViz("digraph {
graph [layout = dot, rankdir = LR]
# define the global styles of the nodes. We can override these in box if we wish
node [shape = rectangle, style = filled, fillcolor = Linen]
data1 [label = <<b>Varied Training</b>  
<br ALIGN = 'LEFT' /> 800-1000
<br/> 1000-1200
<br/>1200-1400>]
data2 [label = <<b>Constant Training</b>  
<br/> 800-1000 >]
Test1 [label = <<b>Testing - No Feedback</b>  
<br ALIGN = 'LEFT' /> 100-300
<br/> 350-550
<br/>600-800>]
Test2 [label = <<b>Test From Train</b>  
<br ALIGN = 'LEFT' /> 800-1000
<br/> 1000-1200
<br/>1200-1400>]
Test3[label = <<b>Testing -Feedback</b>  
<br ALIGN = 'LEFT' /> 100-300
<br/> 350-550
<br/>600-800>]

# edge definitions with the node IDs
{data1 data2}  -> Test1 -> Test2 -> Test3
}
",width=700,height=250)

@@

```{r}
#| column: page-inset-right
#| tbl-cap: "Mean Vx over blocks. Mean (Standard Error)"
#| tbl-cap-location: top

@@

## Testing
```{r}

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7)

# Update this plot code so that the bars are textured to reflect where the testing band is extrapolation, interpolation, or trained. The constant group trained from 800-100 only, while the varied group trained from 800-1000, 1000-1200, 1200-1400.

@@

```{r}
# non linear learning models

>>>>

---
title: Experiment 1 Analysis
date: last-modified
categories: [Analysis, R]
page-layout: full
fig-width: 15
fig-height: 8
code-fold: show
code-tools: true
toc: false
execute: 
  warning: false
  eval: true
---

```{r setup}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt)
e1 <- readRDS(here("data/e1_07_04_23.rds"))
source(here("Functions/Display_Functions.R"))

## Dictionary

@@

## Methods

@@

```{dot}
//| label: fig-simple
//| fig-cap: "This is a simple graphviz graph."
//| fig-width: 8.0
//| fig-height: 2.5
//| fig-responsive: false
digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled]

  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]

  // edge definitions with the node IDs
  data1 -> Test1
  data2 -> Test1

  subgraph cluster {
    label = "Test Phase \n(Counterbalanced Order)"
    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
    Test1 -> Test2
  }

  Test2 -> Test3
}
#https://renenyffenegger.ch/notes/tools/Graphviz/examples/index
#https://edotor.net/
```

@@

```{r}
#| tbl-cap: "Mean Vx over blocks. Mean (Standard Error)"
#| tbl-cap-location: top

@@

## Testing

::: panel-tabset

### Varied vs. Constant
```{r}
#| column: page-inset-right
e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |>  
  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) 
```
### Dist
```{r}
e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |>  ggplot(aes(x = condit, y = dist,fill=vb)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7)

@@

### Vx
```{r}

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |>  ggplot(aes(x = condit, y = vx,fill=vb)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7)

```
:::

```{r}
#| eval: false
# non linear learning models
